### 2018-04-04 tex/paper.tex
Fix typo and clarify

Since the current version of Marlowe follows the `pull' model, a contract written in Marlowe could also be potentially
compiled to a contract written in Ethereum. This could be done in two ways, it could be compiled so that an Ethereum
contract represents a single instance of the contract (with a fixed set of participants), or alternatively it would be
possible to create a generic contract with an extra ``instantiate'' operation that sets-up' a new contract instance
with a given set of participants (represented by a set of public keys).

>>>>

Since the current version of Marlowe follows the `pull' model, a contract written in Marlowe could also be potentially
compiled to a smart-contract written in Ethereum. This could be done in two ways, it could be compiled so that an 
smart-contract represents a single instance of the Marlowe contract (with a fixed set of participants), or 
alternatively it would be possible to create a generic smart-contract with an extra ``instantiate'' operation that 
sets-up a new Marlowe contract instance with a given set of participants (represented by a set of public keys).
